A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-06 latex/main.tex
Updates from Overleaf

During primary inference, gap characters (``-'') are masked 
out as missing data, but this excludes both important information
about deletions from the ARG as well as potentially informative 
phylogenetic signal. 
We therefore performed post-hoc parsinony mapping at 163 sites to include 
the effects of deletions and to ensure that all Pango-informative
sites are included in the ARG.
Using deletions with a minimum frequency of 1\%
(count of sequences divided by 9,149,680 sequences analyzed)
from Table S1 of Li et al.\cite{Li2023indels},
we chose 75 sites to remap.
In addition, we remapped data at 88 sites that were excluded
from primary inference and are defined as Pango lineage 
defining sites by Freyja\cite{Karthikeyan2022}
(\url{https://raw.githubusercontent.com/andersen-lab/Freyja/refs/heads/main/freyja/data/lineage\_mutations.json}).
Alignment data for these 163 sites was then mapped to the 
ARG using the Fitch-Hartigan algorithm\cite{Fitch1971toward,Hartigan1973minimum}
implemented in tskit, including the gap character as a state 
along with the four nucleotides.
Following this, we iteratively applied the node parsimony 
heuristics in sc2ts until there were no further reductions in 
the numbers of mutations.

>>>>

During primary inference, gap characters (``-'') are masked 
out as missing data, but this excludes both important information
about deletions from the ARG as well as potentially informative 
phylogenetic signal. 
We therefore performed post-hoc parsimony mapping at 163 sites to include 
the effects of deletions and to ensure that all Pango-informative
sites are included in the ARG.
Using deletions with a minimum frequency of 1\%
(count of sequences divided by 9,149,680 sequences analyzed)
from Table S1 of Li et al.\cite{Li2023indels},
we chose 75 sites to remap.
In addition, we remapped data at 88 sites that were excluded
from primary inference and are defined as Pango lineage 
defining sites by Freyja\cite{Karthikeyan2022}
(\url{https://raw.githubusercontent.com/andersen-lab/Freyja/refs/heads/main/freyja/data/lineage\_mutations.json}).
Alignment data for these 163 sites was then mapped to the 
ARG using the Fitch-Hartigan algorithm\cite{Fitch1971toward,Hartigan1973minimum}
implemented in tskit, including the gap character as a state 
along with the four nucleotides.
Following this, we iteratively applied the node parsimony 
heuristics in sc2ts until there were no further reductions in 
the numbers of mutations.
